%-------------------------
% Resume in Latex - Single Page Version
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}
\geometry{left=1.2cm, top=0.6cm, right=1.0cm, bottom=0.6cm}
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.2mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{1mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Jayesh Vilas Wankhede}
\newcommand{\phone}{9699424463}
\newcommand{\emailb}{jaywan5588@gmail.com}

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
\parbox{\dimexpr\linewidth\relax}{
\begin{tabularx}{\linewidth}{L r}
  \textbf{\LARGE \name} & +91-\phone \\
  {B.Tech. -- Artificial Intelligence \& Data Science} & \href{mailto:\emailb}{\emailb} \\
  {Vishwakarma Institute of Information Technology, Pune} & \href{https://www.linkedin.com/in/jayesh-wankhede-a-programmer-web-designer/}{\color{blue}LinkedIn} ~|~ \href{https://github.com/jay-3107}{\color{blue}GitHub} \\
\end{tabularx}
}
\vspace{-3mm}

%----------EDUCATION-----------------
\section{Education}
\vspace{1mm}
\textbf{Vishwakarma Institute of Information Technology, Pune} \hfill \textbf{2026} \\
\textit{B.Tech. in Artificial Intelligence \& Data Science} \hfill \textit{CGPA: 8.84} \\
\vspace{0.3mm}
\textbf{MSBTE} \hfill \textbf{2023} \\
\textit{Diploma in Computer Engineering} \hfill \textit{Percentage: 89.66\%}
\vspace{-1mm}

%-----------Technical Skills-----------------
\section{Technical Skills}
\resumeHeadingSkillStart
  \resumeSubItem{Programming}
    {Python, C/C++, OOPS, JavaScript}
  \resumeSubItem{AI/ML \& Data}
    {Machine Learning, Gen AI, LangChain, RAG, Prompt Engineering, Multi-Agent Systems}
  \resumeSubItem{Development}
    {Full Stack (MERN), FastAPI, REST APIs, Git, API Integration, Docker, n8n, Databricks}
  \resumeSubItem{Databases}
    {MySQL, MongoDB, PostgreSQL}
    \vspace{-1mm}
\resumeHeadingSkillEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Syngenta Global Capability Center Private Limited}{}
    {Software Engineer Intern}{Sep 2025 -- Present}
    \resumeItemListStart
        \item {Built a \textbf{multi-agent AI system} with 6 specialized agents (Demand Analyst, Forecast, Scenario Detection, Feature Driver, Model Metrics, Data Drift) orchestrated via \textbf{n8n workflows on Databricks} for demand forecasting across Brazil and Argentina.}
        \item {\textbf{Optimized Scenario Detection Agent}: restructured from 10-node LLM-dependent to 44-node SQL-first pipeline with 5 Databricks SQL queries, reducing per-query LLM token consumption.}
        \item {Integrated a \textbf{Databricks RAG pipeline} for procurement, enabling AI-powered search across supplier data, pricing, and SLA contracts --- deployed end-to-end.}
        \item {Built \textbf{evaluation and test suites} across all 6 agents covering forecast accuracy, scenario correctness, and data drift detection.}
        \item {Developed Python scripts to \textbf{automate n8n workflow deployment} across dev and production; mitigated \textbf{SQL injection} risks in Forecast and Data Drift agents.}
        \item {Refactored scenario selection from \textbf{hardcoded Argentina-specific to dynamic multi-country} architecture; conducted SLA experimentation with stakeholder feedback loops.}
    \resumeItemListEnd

  \resumeSubheading
    {Dravita Pvt. Ltd.}{}
    {Software Developer}{}
    \resumeItemListStart
        \item {Built backend for \textbf{Healthree}, a digital healthcare platform with personalized nutrition planning and product-scan dietary recommendations using Python and \textbf{Docker/Azurite}.}
        \item {Integrated \textbf{Ayushman Bharat Digital Mission (ABDM)} APIs for secure access to medical documents across hospitals.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProject
  {AI-Powered E-Commerce Recommendation System} %Project Name
  {SQL AI Agent for Personalized Product Recommendations} %Subtitle
  {} %Event Dates
  {\href{https://recommendationsystem-frontend.onrender.com/}{\color{blue}Website} ~|~ \href{https://github.com/jay-3107/RecommendationSystem}{\color{blue}GitHub}}
  \resumeItemListStart
    \item {Built an AI-driven chatbot using \textbf{LangChain + Groq Llama-3.3-70B} that handles natural language queries for products, ratings, orders, and cart --- with SQL-based data retrieval on a MERN + SQLite stack.}
  \resumeItemListEnd

\resumeProject
  {Website Chatbot for Indian Aviation Academy (IAA)} %Project Name
  {NLP-Powered Q\&A Chatbot with RAG Pipeline} %Subtitle
  {} %Event Dates
  {\href{https://github.com/jay-3107/IAA}{\color{blue}GitHub}}
  \resumeItemListStart
    \item {Implemented a quantized \textbf{LLaMA 3.1 model with RAG pipeline} on a MERN stack, delivering contextual responses from an admin-managed Q\&A dataset --- reduced need for frequent model fine-tuning.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeHeadingSkillStart
 \resumeSubItem{Full Stack Development}
    {JavaScript, MySQL, CSS \color{blue}{\href{https://drive.google.com/file/d/1Or_knG6CGqp8PKmoV-nXdrPdreg6mVx4/view}{Certificate}}}
 \resumeSubItem{IBM Gen AI}
    {\color{blue}{\href{https://coursera.org/share/310839f1d45ce4adc938be58b01e2875}{Certificate}}}
\resumeHeadingSkillEnd

\end{document}